NTM CT Scoring - Initial Agreement

### 2023-05-17 Stacey Martiniano/ntm_agreement.qmd
GS Kappas done

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
# Select relevant columns, convert to long data
data <- data %>%
  arrange(scan_id, scorer) %>%
  filter(scan_id > 2) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6)
data <- data %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
data$location <- factor(data$location,
  levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", "lul", "rll", "rml", "rul"),
  labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
data$value <- factor(data$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
vals <- levels(data$value)
# One column per scorer
data <- data %>% pivot_wider(names_from = scorer, values_from = value)
# Find disagreements
data$disagree <- !(data$AF == data$DL & data$DL == data$JW)
# Set colors for whole document
n <- length(vals)
name <- "Accent"
colors <- brewer.pal(n, name)
names(colors) <- vals
custom_colors <- scale_fill_manual(name = "", values = colors)
```

# All disagreements

The table below is sortable and searchable, and includes only the features and locations where there was some disagreement.

```{r}
# Table
data %>%
  filter(disagree == T) %>%
  select(-disagree) %>%
  datatable(., rownames = F)
```

# Plots

## All scans

```{r}
data %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_grid(rows = vars(scan_id), cols = vars(feature))
```

@@

```{r}
scan <- 3
data %>%
  filter(scan_id == scan) %>%
  select(feature, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~feature)
```

@@

```{r}
scan <- 4
data %>%
  filter(scan_id == scan) %>%
  select(feature, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~feature)
```

@@

```{r}
scan <- 5
data %>%
  filter(scan_id == scan) %>%
  select(feature, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~feature)
```

# Agreement by Feature

## Atelectasis

```{r}
feat <- "Atelectasis"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Bronchiectasis

```{r}
feat <- "Bronchiectasis"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Cavity

```{r}
feat <- "Cavity"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Consolidation

```{r}
feat <- "Consolidation"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Cyst

```{r}
feat <- "Cyst"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Ground Glass

```{r}
feat <- "Ground Glass"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Mucoid Impaction

```{r}
feat <- "Mucoid Impaction"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Nodule

```{r}
feat <- "Nodule"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Tree in Bud

```{r}
feat <- "Tree In Bud"
# Statistics
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

# Bootstrap

To calculate bootstrap CIs for an kappa, we generated 1000 bootstrap samples clustered by scan ID and location, and calculated Fleiss' $\kappa$ for each bootstrap sample. Percentile and bias-corrected and accelerated (BCa) intervals are presented below.

```{r}
library(boot)
boot_fleiss <- function(df, i) {
  d <- df[i,c("AF","DL","JW")] # allows boot to select sample
  k = kappam.fleiss(d)
  return(k$value)
}
```

```{r}
# Remove scans and features with no variability
df_list = split.data.frame(data,f = ~ scan_id + feature)
perfect_agreement = lapply(df_list,function(d){
  if(all(d$disagree==FALSE) | all(d$disagree==TRUE)){
    return(names(d))
  } else {
    return(NA)
  }
})
boot_df = data
```

## Kappa

### Overall

```{r}
ka <- boot(data,boot_fleiss,R=1000,strata = interaction(factor(data$scan_id),factor(data$location)))
ci=boot.ci(ka,type = c("perc","bca"))
```

Fleiss' $\kappa$ across all features was `r round(ci$t0,3)` (percentile CI: `r paste(round(ci$percent[4],3),"-",round(ci$percent[5],3))`, BCa CI: `r paste(round(ci$bca[4],3),"-",round(ci$bca[5],3))`)

## Tetra/polychoric correlation

@@

@@

## Random effects

In this scenario we have multiple crossed random effects. Each scan contains every level of feature and region, and each level of feature contains each level of region (or vice versa).

```{r}
library(lme4)
library(performance)
# Long data for lmer
re_data_no_bronch = data %>% select(-disagree) %>% 
  filter(feature != "Bronchiectasis") %>% # Remove bronchiectasis because it's on a different scale?
  pivot_longer(AF:JW)
re_data_no_bronch$value = factor(as.character(re_data_no_bronch$value),levels = c("Unchecked", "Checked"))
# Logistic model
m = glmer(value~name+(1|scan_id)+(1|feature)+(1|location),
         data = re_data_no_bronch,family="binomial")
summary(m)
# Logistic model
m2 = glmer(value~name+(1|scan_id)+(1|feature),
         data = re_data_no_bronch,family="binomial")
summary(m2)
icc(m2)
icc(m2,by_group = T)
```

There is essentially no variability in the random effect for location (which I think is good?).

>>>>

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
                  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
data$scan_id = as.numeric(data$scan_id)
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
data$scorer[data$scorer=="GG"]="GS"
# Revert duplicate IDs back to original to match with gold standard
training = read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/training.key.csv")
dups = read.csv("~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/duplicated.key.csv")
training$Training_id = as.numeric(sub("T00","",training$Training_id))
# Change duplicates to OG IDs
old <- dups$duplicated_ssid..dates.shifted..17.days.
new <- dups$original_ssid
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
# Change training IDs to OG IDs
old <- training$Training_id
new = training$Cffid.Scoring.Set
data$scan_id[data$scan_id %in% old] <- new[match(data$scan_id, old, nomatch = 0)]
```

| Cohen's Kappa | Interpretation         |
|---------------|------------------------|
| 0             | No agreement           |
| 0.10 - 0.20   | Slight agreement       |
| 0.21 - 0.40   | Fair agreement         |
| 0.41 - 0.60   | Moderate agreement     |
| 0.61 - 0.80   | Substantial agreement  |
| 0.81 - 0.99   | Near perfect agreement |
| 1             | Perfect agreement      |

# Comparison to gold standards
# Gold standard data
gs = data %>% 
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% training$Cffid.Scoring.Set) %>%
  group_by(scorer,scan_id) %>%
  slice_max(scoresheet_timestamp) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  ungroup()
# Plot colors
name <- "Accent"
colors <- brewer.pal(6, name)
names(colors) <- c("Checked","Unchecked","Absent","Cylindric","Varicose",NA)
custom_colors <- scale_fill_manual(name = "", values = colors)
# Function
compare = function(df,scan_num){
  id = training$Cffid.Scoring.Set[training$Training_id == scan_num]
  df = df %>% filter(scan_id == id)
  df = df %>% pivot_longer(bronchiectasis_rul:atelectasis___6,
                           names_to = c("feature", "location"),
                           names_pattern = "(.*)_(.*)$"
  ) %>% 
    mutate(
      feature = gsub("__", "", feature),
      feature = str_to_title(gsub("_", " ", feature))
    ) 
  df$location <- factor(df$location,
                        levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", 
                                   "lul", "rll", "rml", "rul"),
                        labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", 
                                   "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
  )
  df$value <- factor(df$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
  # One column per scorer
  df <- df %>% 
    pivot_wider(names_from = scorer, values_from = value) %>%
    arrange(feature,location)
  # Kappa for the whole scan
  fk = kappam.fleiss(df[,c("AF","DL","GS","JW")])
  af = kappa2(df[,c("AF","GS")])
  dl = kappa2(df[,c("DL","GS")])
  jw = kappa2(df[,c("JW","GS")])
  cat("\n")
  cat("### Overall")
  cat("\n")
  p = df %>%
    select(feature, location, AF:JW) %>%
    pivot_longer(AF:JW) %>%
    ggplot(., aes(x = name, y = location, fill = value)) +
    geom_tile(color = "black") +
    theme_bw() +
    labs(fill = "", x = "Scorer", y = "Location") +
    custom_colors +
    facet_wrap(~feature)
  cat("\n")
  print(p)
  cat("\n")
  cat("\n")
  cat("Overall Fleiss' Kappa for this scan was ",round(fk$value,3)," (p = ",
      format.pval(fk$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for AF vs. the gold standard"," was ",round(af$value,3)," (p = ",
      format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for DL vs. the gold standard"," was ",round(dl$value,3)," (p = ",
      format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for JW vs. the gold standard"," was ",round(jw$value,3)," (p = ",
      format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  # Analyze by feature
  cat("\n")
  cat("### By Feature and Scorer")
  cat("\n")
  invisible(lapply(levels(factor(df$feature)), function(f){
    t = data.frame(df[df$feature == f,c("AF","DL","GS","JW")])
    rownames(t) = as.character(df$location[df$feature == f])
    fk = kappam.fleiss(t)
    af = kappa2(t[,c("AF","GS")])
    dl = kappa2(t[,c("DL","GS")])
    jw = kappa2(t[,c("JW","GS")])
    p = df %>%
      filter(feature == f) %>%
      select(location, AF:JW) %>%
      pivot_longer(AF:JW) %>%
      ggplot(., aes(x = name, y = location, fill = value)) +
      geom_tile(color = "black") +
      theme_bw() +
      labs(fill = "", x = "Scorer", y = "Location") +
      custom_colors +
      ggtitle(f)
    cat("\n")
    cat("\n")
    cat("####",f)
    cat("\n")
    cat("\n")
    print(p)
    cat("\n")
    cat("\n")
    cat("Fleiss' Kappa for ",f," was ",round(fk$value,3)," (p = ",
        format.pval(fk$p.value,eps = 0.001,digits = 3),")",sep = "")
    cat("\n")
    cat("\n")
    if(is.nan(af$value)){
      cat("\n")
      cat("Agreement between AF and the gold standard in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for AF vs. the gold standard in ",f," was ",round(af$value,3)," (p = ",
          format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(dl$value)){
      cat("\n")
      cat("Agreement between DL and the gold standard in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for DL vs. the gold standard in ",f," was ",round(dl$value,3)," (p = ",
          format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(jw$value)){
      cat("\n")
      cat("Agreement between JW and the gold standard in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for JW vs. the gold standard in ",f," was ",round(jw$value,3)," (p = ",
          format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
  }))
}

## Scan 1

```{r results='asis',warning=FALSE}
compare(df = gs,scan_num = 1)
```

## Scan 2

```{r results='asis',warning=FALSE}
compare(df = gs,scan_num = 2)
```

@@

```{r results='asis',warning=FALSE}
compare(df = gs,scan_num = 3)
```

@@

```{r results='asis',warning=FALSE}
compare(df = gs,scan_num = 4)
```

@@

```{r results='asis',warning=FALSE}
compare(df = gs,scan_num = 5)
```

```{r}
# Save dataset
write.csv(gs,"~/Documents/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/gold_standard_comp.csv",row.names = F,na="")
```

# Duplicates

@@

# Gold standard data
dup_df = data %>% 
  arrange(scan_id, scorer) %>%
  filter(scan_id %in% dups$original_ssid) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  ungroup()
# Function
compare = function(df,scan_num){
  df = df %>% filter(scan_id == scan_num) %>%
    group_by(scorer,scan_id) %>%
    mutate(n = row_number()) %>% ungroup() %>%
    pivot_longer(bronchiectasis_rul:atelectasis___6,
                           names_to = c("feature", "location"),
                           names_pattern = "(.*)_(.*)$"
  ) %>% 
    mutate(
      feature = gsub("__", "", feature),
      feature = str_to_title(gsub("_", " ", feature))
    ) 
  df$location <- factor(df$location,
                        levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", 
                                   "lul", "rll", "rml", "rul"),
                        labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", 
                                   "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
  )
  df$value <- factor(df$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
  # One column per scorer
  df <- df %>% 
    pivot_wider(names_from = scorer, values_from = value) %>%
    arrange(feature,n,location)
  # Kappa for the whole scan
  fk = kappam.fleiss(df[,c("AF","DL","GS","JW")])
  af = kappa2(df[,c("AF","GS")])
  dl = kappa2(df[,c("DL","GS")])
  jw = kappa2(df[,c("JW","GS")])
  cat("\n")
  cat("### Overall")
  cat("\n")
  p = df %>%
    select(feature, location, AF:JW) %>%
    pivot_longer(AF:JW) %>%
    ggplot(., aes(x = name, y = location, fill = value)) +
    geom_tile(color = "black") +
    theme_bw() +
    labs(fill = "", x = "Scorer", y = "Location") +
    custom_colors +
    facet_wrap(~feature)
  cat("\n")
  print(p)
  cat("\n")
  cat("\n")
  cat("Overall Fleiss' Kappa for this scan was ",round(fk$value,3)," (p = ",
      format.pval(fk$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for AF vs. the gold standard"," was ",round(af$value,3)," (p = ",
      format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for DL vs. the gold standard"," was ",round(dl$value,3)," (p = ",
      format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  cat("\n")
  cat("Cohen's Kappa for JW vs. the gold standard"," was ",round(jw$value,3)," (p = ",
      format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
  cat("\n")
  # Analyze by feature
  cat("\n")
  cat("### By Feature and Scorer")
  cat("\n")
  invisible(lapply(levels(factor(df$feature)), function(f){
    t = data.frame(df[df$feature == f,c("AF","DL","GS","JW")])
    rownames(t) = as.character(df$location[df$feature == f])
    fk = kappam.fleiss(t)
    af = kappa2(t[,c("AF","GS")])
    dl = kappa2(t[,c("DL","GS")])
    jw = kappa2(t[,c("JW","GS")])
    p = df %>%
      filter(feature == f) %>%
      select(location, AF:JW) %>%
      pivot_longer(AF:JW) %>%
      ggplot(., aes(x = name, y = location, fill = value)) +
      geom_tile(color = "black") +
      theme_bw() +
      labs(fill = "", x = "Scorer", y = "Location") +
      custom_colors +
      ggtitle(f)
    cat("\n")
    cat("\n")
    cat("####",f)
    cat("\n")
    cat("\n")
    print(p)
    cat("\n")
    cat("\n")
    cat("Fleiss' Kappa for ",f," was ",round(fk$value,3)," (p = ",
        format.pval(fk$p.value,eps = 0.001,digits = 3),")",sep = "")
    cat("\n")
    cat("\n")
    if(is.nan(af$value)){
      cat("\n")
      cat("Agreement between AF and the gold standard in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for AF vs. the gold standard in ",f," was ",round(af$value,3)," (p = ",
          format.pval(af$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(dl$value)){
      cat("\n")
      cat("Agreement between DL and the gold standard in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for DL vs. the gold standard in ",f," was ",round(dl$value,3)," (p = ",
          format.pval(dl$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
    if(is.nan(jw$value)){
      cat("\n")
      cat("Agreement between JW and the gold standard in",f,"was perfect.")
      cat("\n")
    } else {
      cat("\n")
      cat("Cohen's Kappa for JW vs. the gold standard in ",f," was ",round(jw$value,3)," (p = ",
          format.pval(jw$p.value,eps = 0.001,digits = 3),")",sep = "")
      cat("\n")
    }
  }))
}

@@
